---
title: "Publication Figures -- Reviewed"
author: "Maya Lapp"
date: "7/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
#setwd("~/Documents/coding_projects/IS_organized/analysis")
library(tidyverse)
library(grid)
library(gridExtra)
library(ggpubr)
library(colorspace)
library(png)

savePlots = TRUE # determine if running this file should save new plots 
```

Notes: in this file, the following labels are used for simulation dataframes: 
 * `vallino` indicates data from the C&E model original code
 * `vallinoCorrected` indicates data from the corrected version of the C&E model (as described in the ODD framework)
 * `revised` indicates data from the M&S model (as described in the ODD framework)
 * no label (e.g. `allData`) indicates data from the M&S model with dynamic loggers
 
```{r setupData, warning=FALSE}
source(file="dataCleaningFunctions.R") # file containing all functions needed for data cleaning process
load(file = "./allData_IS/MS_model_data_clean.RData") # file loading M&S model data
load(file = "./allData_IS/CE_model_data_clean.RData") # file loading C&E model data
load(file = "./allData_IS/CE_Corrected_model_data_clean.RData") # file loading C&E corrected model data
load(file = "./allData_IS/MS_revised_model_data_clean.RData") # file loading M&S revised model data
endogInst_data = read.csv("./allData_IS/endogInst_model_run.csv")%>%mutate(Period = 1:2001)  # loads a single run of the Endogenous Institution model 
oneThirdBmaxData = read_csv("./allData_IS/one-third-bmax.csv") # loads a single run of Endogenous Institution model with reference-threshold = 1/3 bmax
logger_removal_data = read.csv("./allData_IS/log1000.csv")%>%mutate(cummulativeCheaters=cumsum(numCheaters), period = 1:2001)# load single run of C&E model with 1000 loggers to demonstrate removal of loggers 
ce_corrected_logger_removal_data = read.csv("./allData_IS/CE_corrected_log1000.csv")[1:2001,]%>%mutate(cummulativeCheaters=cumsum(numCheaters), period = 1:2001)# load single run of C&E model with 1000 loggers to demonstrate removal of loggers 
```

```{r graphSettings}
# Setup default plot settings 

# select sizes for text and geoms on plots 
axlab_size <- 12
axtick_size <- 10
point_size = 3
line_size = 1.2
  
# create axes labels that are used repeatedly 
ax_kf = expression(paste(bolditalic("final-institution "),bold("("), K[f], bold(")"))) # final-institutions (Kf)
axlab_bm<-"Biomass (% remaining)"
axlab_density <- "Density"
axlab_time <- "Period"
axlab_perc <- "Percent remianing"
ax_sanc = expression(bolditalic(sanction-level))
ax_mon = expression(bolditalic(monitoring-level))
ax_rt=expression(bolditalic("reference-threshold"))
ax_surveillance=expression(bold(bolditalic("surveillance-level")))
ax_mc=expression(bold(bolditalic("minimum-cut")))
ax_k=expression(paste(bold(bolditalic("current-institution ")), bold("(K)"))) # current-institution (K)



# setup theme for all graphs to follow 
setGraphs<- theme_bw()+
  theme(axis.text=element_text(size=axtick_size, color="black"),
        axis.title=element_text(size=axlab_size,face="bold", color="black"), legend.text = element_text(size=axtick_size))+
  theme(panel.border = element_blank(), axis.line = element_line(colour = "black"))


# setup color theme
color="Set2"
colorDiscrete = scale_color_brewer(palette="Set2")
colorCont = scale_color_viridis_c(option = "magma")
#fillDiscrete = scale_fill_brewer(palette="Dark2")
fillDiscrete = scale_fill_brewer(palette="Set2")
fillCont = scale_fill_viridis_c(option = "magma")

# first two colors in Dark2
#1b9e77
#d95f02

# first 3 colors in Set2 (so can be used independently for figures)
color1="#66c2a5"
color2="#fc8d62"
color3="#8da0cb"

# other good color themes
# scale_color_colorblind()
# scale_color_OkabeIto()

fig = 4 # count figure number for Rmarkdown report 
```


```{r screenshot, eval=FALSE}
s_start = readPNG("./figs/screenshot_beginning.png")%>%rasterGrob()
s_end = readPNG("./figs/screenshot_end.png")%>%rasterGrob()
void = ggplot()+theme_void()
screenshots = grid.arrange(void+ ggtitle("a)"), s_start, void+ ggtitle("b)"), s_end,widths = c(1,10, 1, 10))

if(savePlots) ggsave("./figs/screenshots.pdf", screenshots, width=5.75, height=3.5, units="in")
fig = fig+1
```

### Figure `r fig`
Bravo single run
```{r bravoRun}
instChange = 17 # to make verticle line where institution changes (17 is for this specific simulation run. may be different for a different simulation run)
maxBM = endogInst_data$TotalBM[1] # initial BM in the simulation 
endogInst_data = endogInst_data%>%mutate(TotalBM = TotalBM/maxBM) # convert Total BM to % remaining
endogInst_run_data = endogInst_data%>%filter(Period <= 200) # filter out beginning of simulation 

# plot of K
v1b<-endogInst_run_data%>%ggplot(aes(x=Period))+
  geom_path(aes(y=K),  size=line_size)+
  labs(x=element_blank(), y=ax_k)+
  geom_vline(xintercept = instChange, linetype="dashed", color="dimgrey")+
  ylim(0,20)+
  setGraphs

# plot of average minimal-cut
ax = expression(bold(paste("Avg. ", bolditalic("minimal-cut"))))
v2b<-endogInst_run_data%>%ggplot(aes(x=Period))+
  geom_path(aes(y=k.i),  size=line_size)+
  geom_vline(xintercept = instChange, linetype="dashed", color="dimgrey")+
  labs(x=element_blank(), y=ax)+
  ylim(0,20)+
  setGraphs

# plot of average reference-trees
ax = expression(bold(paste("Avg. ", bolditalic("reference-trees"))))
v3b<-endogInst_run_data%>%ggplot(aes(x=Period))+
  geom_path(aes(y=beta.i),  size=line_size)+
  geom_vline(xintercept = instChange, linetype="dashed", color="dimgrey")+
  labs(x="", y=ax)+
  ylim(0,1)+
  setGraphs

# plot of BM%
v4b<-endogInst_run_data%>%ggplot(aes(x=Period))+
  geom_path(aes(y=TotalBM*100),  size=line_size)+
  geom_vline(xintercept = instChange, linetype="dashed", color="dimgrey")+
  labs(x="", y=axlab_bm)+
  ylim(0,100)+
  setGraphs


# join plots into one figure 
viz_bravo=grid.arrange(v1b+ggtitle("a)"), v2b+ggtitle("b)"), v4b+ggtitle("c)"), v3b+ggtitle("d)"), nrow=2)
viz_bravo=annotate_figure(viz_bravo,
                bottom = text_grob(expression(bold(Period)), vjust = 0,  size = axlab_size),
)

if(savePlots) ggsave("./figs/viz_bravo2.pdf", viz_bravo, width=5.75, height=4, units="in")
fig = fig+1
```

Check model steady state: 
```{r}
maxBM = endogInst_data$TotalBM[1] # initial BM in the simulation 
endogInst_data = endogInst_data%>%mutate(TotalBM = TotalBM/maxBM) # convert Total BM to % remaining
check_steadstate = endogInst_data%>%filter(Period >= 200) # filter out beginning of simulation 
print(paste("Mean BM%:", round(mean(check_steadstate$TotalBM),3)))
print(paste("SD BM%:", round(sd(check_steadstate$TotalBM),3)))

```



## Original Vallino model analysis 

### Figure `r fig`
Minimal cut polarization - Bravo data 
```{r mcPolarization}
# calculate number of loggers with medium min-cut, as well as who has changed min cut within last 30 periods 
mincut_bravo30 = endogInst_run_data%>%mutate(midMC = 100 - lowMinCut - highMinCut, midMC30 = loggers30Periods - highMC30Periods - lowMC30Periods, highMC = highMinCut, lowMC = lowMinCut)
mincut_bravo30 = mincut_bravo30%>%mutate(new_midMC = midMC-midMC30, new_highMC = highMinCut - highMC30Periods, new_lowMC = lowMinCut - lowMC30Periods)
mincut_bravo30 = mincut_bravo30%>%gather(key = "MC.level", value = "NumLogMC", c(highMC, lowMC, midMC30, new_midMC))%>%select(Period, MC.level, NumLogMC)

# order levels for plot
levels(mincut_bravo30$MC.level) 
mincut_bravo30$MC.level <- ordered(mincut_bravo30$MC.level, levels = c("midMC30","new_midMC","highMC", "lowMC"))

# create labels for legend
labelHigh = expression(paste("High (", italic("minimal-cut"), " > 18)"))
labelLow = expression(paste("Low (", italic("minimal-cut"), " < 2)"))

# plot 
viz_minCutBravo = mincut_bravo30%>%ggplot(aes(x = Period, y = NumLogMC))+
  geom_area(aes(fill = MC.level), size = line_size, alpha = 0.8)+
  labs(y = "Loggers (% of Total)")+
  setGraphs+
  scale_fill_manual(breaks=c("new_midMC", "highMC", "lowMC"),name=ax_mc, labels = c("Not polarized", "High (> 18)", "Low (< 2)"), values = c(lighten(color3, amount = 0.3), color3, color1, color2))+
  theme(legend.text.align = 0)


viz_minCutBravo

if(savePlots) ggsave("./figs/viz_mcPolarization_bravo.pdf", viz_minCutBravo, width=5.75, height=3, units="in")

fig = fig+1

txt = max((mincut_bravo30%>%filter(MC.level == "midMC30"))$NumLogMC)
print(paste("Max Loggers older than 30 periods with medium MC:", round(txt,3), "%"))

```


### Figure `r fig`
Single run with tolerance-threshold = 1/3 bmax - the current-institution oscillates indefinitely 
parameters: endogenous institution, base parameters (bmax = 20), 100,000 ticks 
```{r oneThirdBmax}
bmax = 20 

viz_oneThirdBmax_zoomed = oneThirdBmaxData%>%filter(period >= 6100, period<= 6300)%>%ggplot(aes(x = period, y = K))+
  geom_hline(yintercept = 1/3 * bmax, color = color2, size = 1.5)+ # line for 1/3 bmax
  geom_hline(yintercept = 2/3 * bmax, color = color2, size = 1.5)+ # line for 2/3 bmax
  geom_line()+
  labs(x = "Period", y = ax_kf)+
  setGraphs

viz_oneThirdBmax_zoomed

if(savePlots) ggsave("./figs/viz_oneThirdBmax_zoomed.pdf", viz_oneThirdBmax_zoomed, width=4, height=3, units="in")
fig = fig+1


```

### Figure `r fig`

Logger removal 
```{r}

#  ABM log=1000; data only 
viz_removalLoggers=ce_corrected_logger_removal_data[1:500,]%>%ggplot(aes(x=period))+
  labs(x=axlab_time,y= axlab_perc )+
  geom_path(aes(y=TotalBM/TotalBM[1]*100, color = "Biomass"),size=line_size)+ 
  geom_path(aes(y = numLoggers/numLoggers[1]*100, color = "Loggers remaining"),size=line_size)+
  geom_path(aes(y =  100 - numLoggers/numLoggers[1]*100, color = "Loggers removed"),size=line_size)+
  setGraphs+
  theme(legend.title = element_blank())+
  colorDiscrete

if(savePlots) ggsave("./figs/viz_removalLoggers.pdf", viz_removalLoggers, width=5.5, height=2.5, units="in")
viz_removalLoggers
fig = fig+1

```


## C&E model corrected 

Average BM for C&E corrected model 
```{r}
baseData_vallinoCorrected%>%summarize(mean(TotalBM))*100
``` 

### Figure `r fig`
Number of loggers dominates BM% remaining 
```{r}
enfGraphCorrected=enfData_vallinoCorrected%>%mutate(enfValue=rev(as.factor((as.numeric(variableValue)-1)/10)))
viz_surv = enfGraphCorrected %>% filter(enfValue !=0)%>%ggplot(aes(x = numLoggers*100, y = TotalBM*100, color = enfValue))+
  geom_point(aes(color = enfValue), size = 2, alpha = 0.3)+
  labs(color = ax_mon, x = "Loggers (% remaining)", y = axlab_bm)+
  setGraphs + scale_color_brewer(palette="Spectral")

viz_surv

if(savePlots) ggsave("./figs/viz_vallino_mon.pdf", viz_surv, width=5.75, height=3, units="in")
fig = fig+1
```

Regression
As long as any Enforcement exists, Kf and monitoring-level do not significantly impact BM% 
```{r}
vallinoCorrected_lm_data = enfData_vallinoCorrected%>%mutate(monLevel = (1-as.numeric(as.character(variableValue))/100), anyEnf = ifelse(monLevel!=0, TRUE, FALSE))

vallinoCorrected_lm = lm(TotalBM*100 ~ numLoggers+K+monLevel, data = vallinoCorrected_lm_data)
summary(vallinoCorrected_lm)

vallinoCorrected_lm2 = lm(TotalBM*100 ~ numLoggers+K+monLevel, data = vallinoCorrected_lm_data%>%filter(anyEnf))
summary(vallinoCorrected_lm2)


```


## M&S model

### Figure `r fig`
Kf and BM
```{r}
plot_ms = allData_revised %>% mutate(lowLoggers = param == "log" & (variableValue == "60" | variableValue == "80"))


viz_ms_KBM = plot_ms %>% ggplot(aes(x = K, y = TotalBM*100, color = lowLoggers))+
  geom_point(size = 2)+
  labs(x = ax_kf, y = axlab_bm, color = "")+
    scale_color_manual(breaks=c(TRUE, FALSE), labels = c("60 or 80 Loggers", "All other parameter sets"), values=c(color1, color2))+
  setGraphs#+colorDiscrete

viz_ms_KBM

if(savePlots) ggsave("./figs/viz_vallino_mon.pdf", viz_ms_KBM, width=5.75, height=3, units="in")
fig = fig+1
```


```{r}
# calculate correlations 
corr_base = round(cor(baseData_revised$TotalBM, baseData_revised$K), 3)
corr_all = round(cor(allData_revised$TotalBM, allData_revised$K), 3)
corr_all_logNot60 = round(cor((plot_ms%>%filter(!lowLoggers))$TotalBM, (plot_ms%>%filter(!lowLoggers))$K)
, 3)

print(paste("Correlation for base data:", corr_base))
print(paste("Correlation for all data:", corr_all))
print(paste("Correlation for all data, excluding simulations starting with 60 Loggers:", corr_all_logNot60))

```

### Figure `r fig`
monitoring and sanctioning scatterplots, with mon/sanc = 0.2 and 0.8
```{r m&s_monSanc}
#monitoring plot
viz_mon_2_8 = monitoringData_revised%>% filter(variableValue == 0.2| variableValue == 0.8)%>%ggplot(aes(x= K, y = TotalBM*100))+
  geom_point(aes(color = variableValue))+
  labs(color = ax_mon)+
  ylab(axlab_bm)+
  xlab(ax_kf)+
  setGraphs+
  colorDiscrete+
  #ylim(0,23)+
  #xlim(7.5,15)+
  theme(legend.position="bottom")


# sanctioning plot 
#viz_sanc_2_8 = sanctionData%>% filter(variableValue == 2| variableValue == 8)%>%ggplot(aes(x= K, y = TotalBM*100))+
viz_sanc_2_8 = sanctionData_revised%>% filter(variableValue == 2| variableValue == 8)%>%ggplot(aes(x= K, y = TotalBM*100))+
  geom_point(aes(color = as.factor(as.numeric(as.character(variableValue))/10)))+
  labs(color = ax_sanc)+
  ylab(axlab_bm)+
  xlab(ax_kf)+
  setGraphs+
  colorDiscrete+
  #ylim(4,21)+
  #xlim(7.5,15)+
  theme(legend.position="bottom")

viz_monSanc_2_8=grid.arrange(arrangeGrob(arrangeGrob(viz_mon_2_8+ggtitle("a)"),viz_sanc_2_8+ggtitle("b)"), ncol=2, nrow=1)))

if(savePlots) ggsave("./figs/viz_monSanc.2.8.pdf", viz_monSanc_2_8, width=6.5, height=3, units="in")

fig = fig+1

```



linear regressin models 
```{r}

mon_sanc_data = allData_revised%>%filter(param == "monitoring" | param == "sanction")%>%mutate(monitoring = ifelse(param == "monitoring", as.numeric(as.character(variableValue)), 0.5), sanction = ifelse(param == "sanction", as.numeric(as.character(variableValue)), 5)/10 )
mon_sanc_lm = lm(TotalBM*100 ~ K + monitoring + sanction, data = mon_sanc_data)
summary(mon_sanc_lm)
```

### Figure `r fig`
Dynamic Loggers M&S model 
reference-threshold and final-institution relationship scatterplot - with lines of best fit 

```{r calculateNumMeetings, include = FALSE}
#calculating number of meetings for each simulation  

# find max K for each simulation 
x<-maxK(dataRT, seq(1,10, by=1), 2000, 50)

#jumps_test<-findKJumps(dataRT, seq(1,10, by=1), 2000, 50)
numberJumps<-findKJumps(dataRT, seq(1,10, by=1), 2000, 50)
whenFinalJump<-findFinalKJumps(dataRT, seq(1,10, by=1), 2000, 50)

numberJumps2<-numberJumps%>%gather(key="variableValue", value=variableOfInterest)%>%separate(col = variableValue, into = c("type", "variableValue"))

jumpDF<-data.frame(maxK=x, jumps=numberJumps2$variableOfInterest, K=rtData$K, TotalBM=rtData$TotalBM, variableValue=rtData$variableValue, cheaters=rtData$numCheaters)

whenFinalJump2<-whenFinalJump%>%gather(key="variableValue", value=variableOfInterest)%>%separate(col = variableValue, into = c("type", "variableValue"))
rtJumpData<-data.frame(maxK=x, numJumps = numberJumps2$variableOfInterest, finalJump=whenFinalJump2$variableOfInterest, K=rtData$K, TotalBM=rtData$TotalBM, variableValue=rtData$variableValue, cheaters=rtData$numCheaters)

rtJumpData<- rtJumpData%>%mutate(recentMeeting = finalJump>20)
rtJumpData<- rtJumpData%>%mutate(jumpCat = ifelse(as.numeric(numJumps)<2,"once", ifelse(as.numeric(numJumps)<3, "twice","3+ times")))%>%mutate(jumpCat=factor(jumpCat))

```

reference-threshold scatterplot
```{r m&s_rt_kf}
# with recent meetings 
# viz_rt_jump=rtJumpData%>%ggplot(aes(x = as.numeric(variableValue)/10, y = K, color=jumpCat))+
#   geom_point(aes(shape=recentMeeting, size=recentMeeting), position="jitter")+
#   geom_smooth(method='lm', se = FALSE, show.legend = FALSE)+ 
#   scale_color_brewer(palette="Set2",breaks=c("once", "twice", "3+ times"),name="Number of meetings", labels = c("1", "2", "3+"))+
#   scale_shape(name="", breaks=c(TRUE, FALSE), labels=c("Recent meeting", "No recent meeting"))+
#   scale_size_manual(breaks=c(TRUE, FALSE), values=c(2.5,1.5))+
#   labs(x=ax_rt, y=ax_kf)+
#   setGraphs+ 
#   guides(color = guide_legend(override.aes = list(size = 3)), shape = guide_legend(override.aes = list(size = 3)), size=FALSE)

# no recent meetings 
viz_rt_jump=rtJumpData%>%ggplot(aes(x = as.numeric(variableValue)/10, y = K, color=jumpCat))+
  geom_point(position="jitter")+
  geom_smooth(data = rtJumpData%>%filter(jumpCat !="once"), method='lm', se = FALSE, show.legend = FALSE)+ #get rid of data = argument to include regression line for communities that have only met once
  scale_color_brewer(palette="Set2",breaks=c("once", "twice", "3+ times"),name="Number of meetings", labels = c("1", "2", "3+"))+
  labs(x=ax_rt, y=ax_kf)+
  setGraphs+ 
  guides(color = guide_legend(override.aes = list(size = 3)))


viz_rt_jump

if(savePlots) ggsave("./figs/viz_rtJump_removeRedRegression.pdf", viz_rt_jump, width=5.75, height=3, units="in")

fig = fig+1

```


